### 2020-05-28 serial.tex
done

\eref{backward} suggests that backward delay distributions change over time even if their corresponding forward delay distribution does not change.
Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations:
Conditioning on individuals whose secondary events have occurred at the same time means that the distribution is truncated so that we tend to observe shorter (or longer) inter-event delays when incidence is  the cohort size has been increasing (or decreasing) over time.
In particular, when the incidence is growing exponentially, we can calculate the amount of bias exactly.
Assuming that the forward delay distribution remains constant during the exponential growth phase ($f_p(\tau) \approx f_0(\tau)$), we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
\begin{align}
b_0(\tau) &= \left[\psize(0)/\ssize(0)\right] \exp(-r\tau) f_0(\tau)
\label{eq:backexp}
\end{align}
where $r$ is the exponential growth rate (and $\psize(0)/\ssize(0) = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
For faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.
Changes in the backward delay distribution are also by definition affected by the changes in the forward delay distribution (\eref{backward}).
Therefore, the backward delay distribution will generally differ from the forward delay distribution even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distributions.

>>>>

\eref{backward} suggests that backward delay distributions change over time even if their corresponding forward delay distribution does not change.
Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations:
Conditioning on individuals whose secondary events have occurred at the same time means that the distribution is truncated so that we tend to observe shorter (or longer) inter-event delays when incidence is  the cohort size has been increasing (or decreasing) over time.
In particular, when the incidence is growing exponentially, we can calculate the amount of bias exactly.
Assuming that the forward delay distribution remains constant during the exponential growth phase ($f_p(\tau) \approx f_0(\tau)$), we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
\begin{align}
b_0(\tau) &= \left[\psize(0)/\ssize(0)\right] \exp(-r\tau) f_0(\tau)
\label{eq:backexp}
\end{align}
where $r$ is the exponential growth rate (and $\left[\psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
For faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.
Changes in the backward delay distribution are also by definition affected by the changes in the forward delay distribution (\eref{backward}).
Therefore, the backward delay distribution will generally differ from the forward delay distribution even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distributions.
